Component response rate variation drives stability in large complex systems

### 2018-06-18 notebook/arxiv/ms.tex
Fix function in SI, new version now

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{summarise_randmat_ga <-}\StringTok{ }\NormalTok{function(tot_res, fea_res)\{}
    \NormalTok{sims    <-}\StringTok{ }\KeywordTok{length}\NormalTok{(tot_res);}
    \NormalTok{all_res <-}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DataTypeTok{data =} \DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \NormalTok{sims, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{);}
    \NormalTok{for(i in }\DecValTok{1}\NormalTok{:sims)\{}
        \NormalTok{unstables <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE} \NormalTok{&}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE}\NormalTok{;}
        \NormalTok{stables   <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}  \NormalTok{&}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}\NormalTok{;}
        \NormalTok{unstabled <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}  \NormalTok{&}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE}\NormalTok{;}
        \NormalTok{stabled   <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE} \NormalTok{&}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}\NormalTok{;}
        \NormalTok{non_feas  <-}\StringTok{ }\NormalTok{fea_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE} \NormalTok{&}\StringTok{ }\NormalTok{fea_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE}\NormalTok{;}
        \NormalTok{feasibl   <-}\StringTok{ }\NormalTok{fea_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}  \NormalTok{&}\StringTok{ }\NormalTok{fea_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}\NormalTok{;}
        \NormalTok{unfeased  <-}\StringTok{ }\NormalTok{fea_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}  \NormalTok{&}\StringTok{ }\NormalTok{fea_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE}\NormalTok{;}
        \NormalTok{feased    <-}\StringTok{ }\NormalTok{fea_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE} \NormalTok{&}\StringTok{ }\NormalTok{fea_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}\NormalTok{;}
        \NormalTok{foundd    <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{3}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}\NormalTok{;}
        \NormalTok{all_res[i, }\DecValTok{1}\NormalTok{]  <-}\StringTok{ }\NormalTok{i +}\StringTok{ }\DecValTok{1}\NormalTok{;}
        \NormalTok{all_res[i, }\DecValTok{2}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(unstables);}
        \NormalTok{all_res[i, }\DecValTok{3}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(stables);}
        \NormalTok{all_res[i, }\DecValTok{4}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(unstabled);}
        \NormalTok{all_res[i, }\DecValTok{5}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(stabled);}
        \NormalTok{all_res[i, }\DecValTok{6}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(non_feas);}
        \NormalTok{all_res[i, }\DecValTok{7}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(feasibl);}
        \NormalTok{all_res[i, }\DecValTok{8}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(unfeased);}
        \NormalTok{all_res[i, }\DecValTok{9}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(feased);}
        \NormalTok{all_res[i, }\DecValTok{10}\NormalTok{] <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(foundd);}
    \NormalTok{\}}
    \KeywordTok{return}\NormalTok{(all_res);}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{summarise_randmat <-}\StringTok{ }\NormalTok{function(tot_res, fea_res)\{}
    \NormalTok{sims    <-}\StringTok{ }\KeywordTok{length}\NormalTok{(tot_res);}
    \NormalTok{all_res <-}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DataTypeTok{data =} \DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \NormalTok{sims, }\DataTypeTok{ncol =} \DecValTok{7}\NormalTok{);}
    \NormalTok{for(i in }\DecValTok{1}\NormalTok{:sims)\{}
        \NormalTok{A0_unst   <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE}\NormalTok{;}
        \NormalTok{A0_stbl   <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}\NormalTok{;}
        \NormalTok{A1_unst   <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE}\NormalTok{;}
        \NormalTok{A1_stbl   <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}\NormalTok{;}
        \NormalTok{stabled   <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE} \NormalTok{&}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}\NormalTok{;}
        \NormalTok{unstabled <-}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{1}\NormalTok{] ==}\StringTok{ }\OtherTok{TRUE}  \NormalTok{&}\StringTok{ }\NormalTok{tot_res[[i]][,}\DecValTok{2}\NormalTok{] ==}\StringTok{ }\OtherTok{FALSE}\NormalTok{;}
        \NormalTok{all_res[i, }\DecValTok{1}\NormalTok{]  <-}\StringTok{ }\NormalTok{i +}\StringTok{ }\DecValTok{1}\NormalTok{;}
        \NormalTok{all_res[i, }\DecValTok{2}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(A0_unst);}
        \NormalTok{all_res[i, }\DecValTok{3}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(A0_stbl);}
        \NormalTok{all_res[i, }\DecValTok{4}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(A1_unst);}
        \NormalTok{all_res[i, }\DecValTok{5}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(A1_stbl);}
        \NormalTok{all_res[i, }\DecValTok{6}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(stabled);}
        \NormalTok{all_res[i, }\DecValTok{7}\NormalTok{]  <-}\StringTok{ }\KeywordTok{sum}\NormalTok{(unstabled);}
    \NormalTok{\}}
    \KeywordTok{colnames}\NormalTok{(all_res) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"N"}\NormalTok{, }\StringTok{"A0_unstable"}\NormalTok{, }\StringTok{"A0_stable"}\NormalTok{, }\StringTok{"A1_unstable"}\NormalTok{,}
                           \StringTok{"A1_stable"}\NormalTok{, }\StringTok{"A1_stabilised"}\NormalTok{, }\StringTok{"A1_destabilised"}\NormalTok{);}
    \KeywordTok{return}\NormalTok{(all_res);}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}
